\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-06-03 paper/jitp_rr_memo/jitp_rr_memo.tex
added the discussion of the downsides of the manual approach reviewer 2 asked for

    \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods. We have also revised the conclusion to point specifically to the implications of our contributions. In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.

@@

    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection address this point. See also our responses to R2's comments 1--3.

>>>>

    \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods. We have also added a discussion of the manual content analysis and its downsides in the e-government literature (as well as a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues) to the end of the literature section. Finally, we revised the conclusion to point specifically to the implications of our contributions. In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.

@@

    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection at the end of the literature section address this point. See also our responses to R2's comments 1--3.

### 2021-06-03 paper/manuscript_jitp_rr.tex
added the discussion of the downsides of the manual approach reviewer 2 asked for

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. The websites of politicians and their parties have also been the object of research \citep{Druckman2009,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S. Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.

>>>>

%This used to say 'The existing research that uses scraped websites', but most of these were actually based on hand-coding
%I also changed the end of the sentence (which was 'an indication of the theoretical value of empirical analysis of web contents') to make it more focused on what R2 wanted

Existing research that analyzes websites \textit{manually} provides an indication of the potential benefits of automated analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. Papers in the e-government literature differ in terms of specific instruments, indices, and items, but they largely follow the same principle: researchers manually visit each website and record whether a feature is present or not \citep{kaylor2001gauging, Urban2002, jeffres2006metropolitan, Armstrong2011, dolson2012explaining, Feeney2017}\footnote{Another literature following a similar approach concerns the websites of politicians and their parties. By and large, researchers in this field also rely on hand-coding \citep{Norris2003,Druckman2009,Druckman2010,Esterling2011}, albeit with some exceptions, who do use targeted scrapers \citep{Therriault2010,cryer2019navigating}.}. This approach is also used by the Rutgers E-Governance Institute, whose survey instrument has influenced the e-government literature at large. \cite{holzer2016digital} have conducted seven studies, between 2003 and 2016, of the largest city's website in each of the world's 100 nations with the most internet users. In each case, evaluators visit each website and manually score it according to 104 items. However, this level of thoroughness comes at a price - \cite{holzer2016digital} name a total of 127 website evaluators in their list of acknowledgements.

This approach is labor-intensive and therefore expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within the narrow confines of their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial resources might struggle to provide a complete understanding of individual websites. Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one. By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.

%For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S. Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.  %removed this sentence for now, but could put it back in the footnote
